Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-10-29 paper/main.tex
artist diag

\begin{figure}[h!]
  \includegraphics[width=\columnwidth]{intersection_f.png}
  \caption{The fiber spaces $F_a, F_b$ have a shared fiber space $F_c$. If they are input into the same artist $A_1$, then an equivariant transformation is one where $F_c$ is transformed to a visual element in a consistent matter. In this figure, $F_c$ is mapped to the x-axis for both $F_a$ and $F_b$.}
  \label{fig:artist:compose:union_fiber}
\end{figure}
an example of expecting consistency in overlapping fields are the multiple view constraints described by Qu and Hullman \cite{hullmanKeeping2018}. 
\begin{equation}
  \label{eq:artist:intersection:fiber}
  \begin{tikzcd}[row sep = .5em]
    \dfiber_a \arrow[rrd, "proj_a" description] \arrow[rrrr, "\vartist_a"] &  &             &  & Im_{\vartist_a} \arrow[lld, "g_a" description, dashed] \\
                                                                           &  & \dfiber_{c} &  &                                                                      \\
    \dfiber_b \arrow[rru, "proj_b" description] \arrow[rrrr, "\vartist_b"] &  &             &  & Im_{\vartist_b} \in \arrow[llu, "g_b" description, dashed]
\end{tikzcd}
\end{equation}

@@

We enforce the equivariance constraint specified in \autoref{eq:artist:construction:multi_nu} by constructing artists that apply \vchannel\ encoders such that 
\begin{equation}
  \label{eq:artist:construction:multi_nu}
  \begin{tikzcd}[row sep=.5em]
    \dfiber_a \arrow[rrd, "proj_a" description] \arrow[rrrr, "\vchannel_{\dfiber_c}"]           &  &  &  & \vfiber_{\dfiber_c}          \\
     &  & \dfiber_{c} \arrow[rru, "\vchannel_{\dfiber_c}" description] \arrow[rrd, "\vchannel^{\prime}_{\dfiber_c}" description] &  &                              \\
    \dfiber_b \arrow[rru, "proj_b" description] \arrow[rrrr, "\vchannel^{\prime}_{\dfiber_c}"'] &  &                                                                                                                        &  & \vfiber^{\prime}_{\dfiber_c}
    \end{tikzcd}
\end{equation}

@@

>>>>

\begin{figure}[h!]
  \includegraphics[width=\columnwidth]{intersection_f.png}
  \caption{The fiber spaces $F_a, F_b$ have a shared fiber space $F_c$. If they are input into the same artist $A_1$, then an equivariant transformation is one where $F_c$ is transformed to a visual element in a consistent matter. In this figure, $F_c$ is mapped to the x-axis for both $F_a$ and $F_b$.}
  \label{fig:artist:compose:union_fiber}
\end{figure}
an example of expecting consistency in overlapping fields are the multiple view constraints described by Qu and Hullman \cite{hullmanKeeping2018}. 
\begin{equation}
  \label{eq:artist:intersection:fiber}
  \begin{tikzcd}
    F_a\times{_{F_c}}F_b     & F_a \arrow[d, "proj_a"] \\
    F_b \arrow[r, "proj_b"'] & F_c                    
    \end{tikzcd}
\end{equation}

@@

We enforce the equivariance constraint specified in \autoref{eq:artist:construction:multi_nu} by constructing artists that apply \vchannel\ encoders such that 
\begin{equation}
  \label{eq:artist:construction:multi_nu}
  \begin{tikzcd}[row sep=.5em]
    \dfiberc_a \arrow[rrd, "proj_a" description] \arrow[rrrr, "\vchannelc_c"]  &  &  &  & \vfiberc_c \\
    &  & \dfiberc_{c} \arrow[rru, "\vchannelc_c" description] \arrow[rrd, "\vchannelc^{\prime}_c" description] &  & \\
    \dfiberc_b \arrow[rru, "proj_b" description] \arrow[rrrr, "{\vchannelc_c}^{\prime}"'] &  &                                                                                                       &  & {\vfiberc_c}^{\prime}
    \end{tikzcd}
\end{equation}

@@

\begin{equation}
  \label{eq:artist:construction:q:multifiber}
\begin{tikzcd}
  \dfiberc_a \arrow[rr, "\vchannelc"] \arrow[rd, "proj_a" description]          &            & \vfiberc_a \arrow[rr, "\vmarkd"]         &  & Im_{\vmarkdc} \subset \gtotalc \arrow[llld, "g_a" description, dashed]                  \\
 & \dfiberc_c &                                          &  &\\
  \dfiberc_b \arrow[rr, "\vchannelc^{\prime}"] \arrow[ru, "proj_b" description] &            & \vfiber_b \arrow[rr, "\vmarkd^{\prime}"] &  & Im_{\vmarkdc^{\prime}}\subset \gtotalc^{\prime} \arrow[lllu, "g_b" description, dashed]
  \end{tikzcd}
\end{equation}
